Limits to Ecological Forecasting: Estimating Uncertainty for Critical Transitions with Deep Learning

### 2022-09-22 manuscript/manuscript.Rmd
Might've missed something

We have created a github repository <https://github.com/boettiger-lab/mee_tipping_point_forecasting.> that contains the code used to produce the figures herein.

>>>>

We have created a github repository <https://github.com/boettiger-lab/mee_tipping_point_forecasting> that contains the code used to produce the figures herein.
